---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nexminer

<!-- badges: start -->
<!-- badges: end -->

The goal of nexminer is to ...

## Installation

You can install the released version of nexminer from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("nexminer")
```

## Example

https://nexushub.co/ provides and [API](https://nexushub.co/developers/api/General/foo) to data mine several prices of in game items of the video game World of Warcraft Classic. The following tool simplifies R users to import the data or loop over several items.

The following examples show how to import price trends of black lotus on the EU server Patchwerk Faction Horde:

```{r example}
library(nexminer)
library(dplyr)
library(ggplot2)

server <- "patchwerk"
fraction <- "horde"

rh_raw <- import_item("rugged hide", server, fraction)
rh_clean <- clean_json(rh_raw)
smooth_item(rh_clean)
lm_item_wday(rh_clean)

```

