---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nexminer

<!-- badges: start -->
<!-- badges: end -->

https://nexushub.co/ provides and [API](https://nexushub.co/developers/api/General/foo) to data mine several prices of in game items of the video game World of Warcraft Classic. The following tool simplifies R users to import the data or loop over several items. Please be reminded that all data is collected by the nexushub team and their development page can be visited [here](https://github.com/nexus-devs/wow-classic-items).

## Install

```{r eval=FALSE}
devtools::install_github("gstephan30/nexminer")
```


## Example


The following examples show how to import price trends of [Black Lotus](https://classic.wowhead.com/item=13468) or [Rugged Hide](https://classic.wowhead.com/item=8171)on the EU server Patchwerk Faction Horde:

```{r example1}
library(nexminer)
library(patchwork)

server <- "patchwerk"
fraction <- "horde"

rh_raw <- import_item("rugged hide", server, fraction)
rh_clean <- clean_json(rh_raw)
p1 <- smooth_item(rh_clean)
p2 <- lm_item_wday(rh_clean)

p1 / p2
```


```{r example2}
bl_raw <- import_item("Black LOTus", server, fraction)
bl_clean <- clean_json(bl_raw)
p3 <- smooth_item(bl_clean)
p4 <- lm_item_wday(bl_clean)

p3 / p4
```

